Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-08 paper/current/main.tex
adding authors"

% Define the supporting information name
\def\SI{Supporting Information}

%}}}

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\date{\today}
\maketitle %}}}

>>>>

% Define the supporting information name
\def\SI{Supporting Information}
\usepackage{authblk}
%}}}

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\author[1,4]{Dakota Murray}
\author[1, 2, 4]{Jisung Yoon}
\author[1]{Sadamori Kojaku}
\author[3]{Rodrigo Costas}
\author[2]{Woo-Sung Jung}
\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
\author[1]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}

\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
2300 AX Leiden, The Netherlands}
\affil[4]{These authors contributed equally: Jisung Yoon, Dakota Murray.}

\date{\today}
\maketitle %}}}
